Cournot Competition with Idiosyncratic Tax

### 2019-02-04 summary.tex
added minor changes to tex file to show you how we can work on the document together.
Implemented Edits Sandro suggested.

\usepackage{dsfont}
\newcommand{\R}{\mathds {R}}
\title{ABM of Cournot Competition with Idiosyncratic Tax}
\author{Nate Dwyer and Sandro Lera}

@@

The 'geography' of our model is one-dimensional with periodic boundaries, 
i.e. a topological circle. We denote the length of that circle by $L$. We 
measure physical distances with the metric $min(|x-y|, L-|y-x|)$ for 
any two points ('agents') $x$,$y$ on $L$. Without loss of generality,
we set $L=1$.

\subsection{Buyers}
On that circle we place some $|B|$ buyers randomly distributed. The buyers
all have an identical demand curve $P=a-Q$, and each buyer $b\in B$ buys a 
quantity $\vec{b}$, where $b_i$ is the amount $b$ buys from the $i$th
seller. Each buyer tries to buy as much total quantity as they can while
staying under the curve, i.e. they try to maximize $sum(\vec{b})$.

@@

\subsection{Profit Function}
The profit function is as follows: $\Pi_i = p_i * q_i^s - c*q_i$, where $c$
is the price to produce each unit of product, and $q_i^s$ is the quantity 
the $i$th seller sells.

\section{Setup}
We construct a set of buyers $B$ and a set of sellers $S$, and transaction cost
function $t: (B\times S)\rightarrow \R$, which has subfunctions $t_b:
S\rightarrow \R$ s.t. for all $s\in S$, $t(b,s) = t_b(s)$.

@@

\section{Function to put into nashpy}
We construct a function $\Pi : (\R\times\R)^{|S|} \rightarrow \R^{|S|}$ s.t.
$\Pi(\vec{s}) = \vec{\pi}$, where the elements of $\vec{s}$ are the tuples
$(q_i,p_i)$ listing the quantity produced and the price offered by the $i$th
seller, and the elements of $\vec{\pi}$ are $\pi_i$, the profits of the $i$th seller.

Given $\vec{s}$, $\vec{\pi}$ is calculated by first calculating $\vec{q}^s$, the
vector of total quantity sold, then using it to calculate $\vec{\pi}$ using the formula $\pi_i = p_iq^s_i$.

@@

Finally, re-index this new vector using the $i$-index instead of the $j$ index
to get $\vec{b}$.
\end{document}

>>>>

\usepackage{dsfont}
\newcommand{\R}{\mathds {R}}
\title{Cournot Competition with Idiosyncratic Tax}
\author{Nate Dwyer and Sandro Lera}

@@

The `geography' of our model is one-dimensional with periodic boundaries, i.e. a
topological circle. We denote the length of that circle by $L$. We measure
physical distances with the metric $min(|x-y|, L-|y-x|)$ for any two points
('agents') $x$,$y$ on $L$. Without loss of generality, we set $L=1$.

\subsection{Buyers}
On that circle we place some $|B|$ buyers randomly distributed. The buyers all
have an identical demand curve $P + Q = a$, and each buyer $b\in B$ buys a quantity
$\vec{b}$, where $b_i$ is the amount $b$ buys from the $i$th seller. Each buyer
tries to buy as much total quantity as they can while keeping $P + Q < a$ i.e.
they try to maximize $\sum_{i=0}^{|S|}b_i$.

@@

\subsection{Profit Function}

The profit function is as follows:
\begin{equation}
    $\Pi_i = p_iq_i^s - cq_i$
\end{equation}
where $c$ is the price to produce each unit of product, and $q_i^s$ is the
quantity the $i$th seller sells.

\section{Mathematical Representation}
We construct a set of buyers $B$ and a set of sellers $S$, and transaction cost
function $t: (B\times S)\rightarrow \R$, which has subfunctions $t_b:
S\rightarrow \R$ s.t. for all $s\in S$, $t(b,s) = t_b(s)$.

@@

\section{Function to put into Gambit}

We construct a function $\Pi : (\R\times\R)^{|S|} \rightarrow \R^{|S|}$ s.t.
$\Pi(\vec{s}) = \vec{\pi}$, where the elements of $\vec{s}$ are the tuples
$(q_i,p_i)$ listing the quantity produced and the price offered by the $i$th
seller, and the elements of $\vec{\pi}$ are $\pi_i$, the profits of the $i$th
seller.

Given $\vec{s}$, $\vec{\pi}$ is calculated by first calculating $\vec{q}^s$, the
vector of total quantity sold, then using it to calculate $\vec{\pi}$ using 
equation (1).

@@

Finally, re-index this new vector using the $i$-index instead of the $j$ index
to get $\vec{b}$.

\end{document}
